Tight battle between republicans and democrats with Kamala in the lead

### 2024-11-04 paper/paper.qmd
Update paper.qmd
Added reference to dataset
Update paper.qmd
Added abstract

---
title: "Tight battle between republicans and democrats with Kamala in the lead"
subtitle: "Pollsters in America are suggesting that Americans prefer Kamala as president"
author: 
  - Chris Yong Hong Sen
  - Veyasan Ragulan
  - Prankit Bhardwaj
thanks: "Code and data are available at: [https://github.com/Monoji77/USA-pollster](https://github.com/Monoji77/USA-pollster)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

The dataset provided by fivethirtyeight contains over 15000 observations across 50 variables. Each observation is a poll conducted on the 2024 US Presidential Election. Fivethirtyeight's dataset was chosen due to it's comprehensive review of polls and pollsters, attributing grades in error and bias, as well as in transparency. Their thorough investigations ensure their dataset not only contains insightful polls, but also includes as much relevant information about the polls conducted as possible. This gives us plenty of predictors when building a model that will caluclate the percentage win of either Trump or Harris.

>>>>

---
title: "Tight battle between republicans and democrats with Kamala in the lead"
subtitle: "Pollsters in America are suggesting that Americans prefer Kamala as president"
author: 
  - Chris Yong Hong Sen
  - Veyasan Ragulan
  - Prankit Bhardwaj
thanks: "Code and data are available at: [https://github.com/Monoji77/USA-pollster](https://github.com/Monoji77/USA-pollster)."
date: today
date-format: long
abstract: "This paper forecasts the 2024 U.S. Presidential Election between Kamala Harris and Donald Trump using linear regression models applied to recent polling data. The analysis projects a win for Harris, who leads Trump by an estimated 5 percentage points on average, with consistent support across most polling organizations and swing states. The models underscore the impact of pollster bias and regional variability on election outcomes. Future research should integrate non-linear modeling and Bayesian methods to improve predictive accuracy."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

The dataset provided by fivethirtyeight [@fivethirtyeight] contains over 15000 observations across 50 variables. Each observation is a poll conducted on the 2024 US Presidential Election. Fivethirtyeight's dataset was chosen due to it's comprehensive review of polls and pollsters, attributing grades in error and bias, as well as in transparency. Their thorough investigations ensure their dataset not only contains insightful polls, but also includes as much relevant information about the polls conducted as possible. This gives us plenty of predictors when building a model that will caluclate the percentage win of either Trump or Harris.
